---
title: How to read mass spectrometry data
author: Laurent Gatto
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{EDIT:HowToTitle}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
    opts_chunk:
        collapse: true
        comment: '#>'
format:
    html:
        toc: true
        html-math-method: mathjax
---

```{r}
#| echo: false

suppressPackageStartupMessages({
    library(BiocStyle)
})
```

EDIT:Short introduction

# Bioconductor packages used in this document

EDIT:Add list of packages used in the HowTo. Use `r Biocpkg("PkgName")` to
refer to Bioconductor packages, and similarly for other package sources
(see https://bioconductor.org/packages/release/bioc/vignettes/BiocStyle/inst/doc/AuthoringRmdVignettes.html#4_Style_macros). Example:


* `r Biocpkg("Spectra")`
* `r Biocpkg("mzR")`
* `r Biocpkg("MsDataHub")`

# How to read mass spectrometry data

Let's first get some example raw mass spectrometry data from the
*MsDataHub* package. Below, we download two _sciex_ mzML files
represent profile-mode LC-MS data of pooled human serum samples and
create a vector of files names `fls`:

```{r}
library(MsDataHub)
fls <- c(X20171016_POOL_POS_1_105.134.mzML(),
         X20171016_POOL_POS_3_105.134.mzML())
fls
```

We can now use the `Spectra()` constructor function to create an
object of class `Spectra` that contains the raw data data. Note that
the `mzR` package is needed to read the content of the mzML files.


```{r}
suppressPackageStartupMessages({
    library("Spectra")
    library("mzR")
})
```

```{r}
sp <- Spectra(fls)
sp
```

The object contains `r length(sp)` spectra from both files.

# Further reading

- The [R for Mass Spectrometry](https://rformassspectrometry.github.io/book/) book.
- The [Large-scale data handling and processing with
  Spectra](https://rformassspectrometry.github.io/Spectra/articles/Spectra-large-scale.html)
  vignette from the *Spectra* package.

# Session info

<details>
<summary><b>
Click to display session info
</b></summary>
```{r}
sessionInfo()
```
</details>
