---
title: EDIT:HowToTitle
author: EDIT:HowToAuthor
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{EDIT:HowToTitle}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
    opts_chunk:
        collapse: true
        comment: '#>'
format:
    html:
        toc: true
        html-math-method: mathjax
---

```{r}
#| echo: false

suppressPackageStartupMessages({
    library(BiocStyle)
})
```

EDIT:Short introduction

# Bioconductor packages used in this document

EDIT:Add list of packages used in the HowTo. Use `r Biocpkg("PkgName")` to
refer to Bioconductor packages, and similarly for other package sources
(see https://bioconductor.org/packages/release/bioc/vignettes/BiocStyle/inst/doc/AuthoringRmdVignettes.html#4_Style_macros). Example:
* `r Biocpkg("pasillaBamSubset")`

# EDIT:Main section

EDIT:Here, put the code and explanations for your HowTo. Keep in mind that
HowTos should be short, and address a well-defined, specific task using
Bioconductor.

# Further reading

EDIT: add a (short) list of useful resources about.

# Session info

<details>
<summary><b>
Click to display session info
</b></summary>
```{r}
sessionInfo()
```
</details>
